### 2022-09-14 README.Rmd
`elmt()` accepts a chracter vector as an  element of `lhs`

## Overview
Empirical likelihood enables a nonparametric, likelihood-driven style of inference without relying on assumptions frequently made in parametric models.
Empirical likelihood-based tests are asymptotically pivotal and thus avoid explicit studentization, making it also challenging for the methods to be directly extended to other packages for parametric models. 
The R package [melt](https://cran.r-project.org/package=melt) aims to bridge the gap and provide a unified framework for data analysis with empirical likelihood methods.
A collection of functions are available to perform multiple empirical likelihood tests and construct confidence intervals for linear and generalized linear models in R.
The package offers an easy-to-use interface and flexibility in specifying hypotheses and calibration methods, extending the framework to simultaneous inference.
The core computational routines are implemented with the [Eigen](https://eigen.tuxfamily.org/index.php?title=Main_Page) C++ library and [RcppEigen](https://cran.r-project.org/package=RcppEigen) interface, with OpenMP for parallel computation. 
Details of the testing procedures are given in [Kim, MacEachern, and Peruggia (2021)](https://arxiv.org/abs/2112.09206). 
This work was supported by the U.S. National Science Foundation under Grants No. [SES-1921523](https://nsf.gov/awardsearch/showAward?AWD_ID=1921523) and [DMS-2015552](https://nsf.gov/awardsearch/showAward?AWD_ID=2015552).

>>>>

## Overview
Empirical likelihood enables a nonparametric, likelihood-driven style of inference without relying on assumptions frequently made in parametric models.
Empirical likelihood-based tests are asymptotically pivotal and thus avoid explicit studentization, making it also challenging for the methods to be directly extended to other packages for parametric models. 
The R package [melt](https://cran.r-project.org/package=melt) aims to bridge the gap and provide a unified framework for data analysis with empirical likelihood methods.
A collection of functions are available to perform multiple empirical likelihood tests and construct confidence intervals for linear and generalized linear models in R.
The package offers an easy-to-use interface and flexibility in specifying hypotheses and calibration methods, extending the framework to simultaneous inferences.
The core computational routines are implemented with the [Eigen](https://eigen.tuxfamily.org/index.php?title=Main_Page) C++ library and [RcppEigen](https://cran.r-project.org/package=RcppEigen) interface, with OpenMP for parallel computation. 
Details of the testing procedures are given in [Kim, MacEachern, and Peruggia (2021)](https://arxiv.org/abs/2112.09206). 
This work was supported by the U.S. National Science Foundation under Grants No. [SES-1921523](https://nsf.gov/awardsearch/showAward?AWD_ID=1921523) and [DMS-2015552](https://nsf.gov/awardsearch/showAward?AWD_ID=2015552).
